The Impact of Educational Expenses of New Coders

### 2021-04-18 outputs/paper/paper.Rmd
Edit a table for descriptive statistics

## Description of Dataset
The original dataset used for this paper is obtained from `freeCodeCamp`’s GitHub page. The format of the dataset is a comma-separated values (CSV) file, which contains 136 columns and 18,175 observations. I selected 8 variables and cleaned the data using the R programming language [@citeR] and the tidyverse package [@cityTidyverse] and the dplyr package [@cityDplyr]. The selected variables are: Age, CityPopulation, CommuteTime, Gender,  Income,  MoneyForLearning,  MonthsProgramming, and SchoolDegree. The CityPopulation is the estimated number of city population of the recipient; the question asked was "About how many people live in your city?”, and there are three options to choose: “less than 100,000”,  "between 100,000 and 1 million", and "more than 1 million". Since these answers were coded as strings, I converted them into numeric variables using the `recode` function of `dplyr` [@cityDplyr]. The answers for CommuteTime and SchoolDegree were also coded as strings in the original dataset, so I applied the same data cleaning process to the variables as I did with CityPopulation. Also, I omitted observations which have a missing value. Table \@ref(tab:tabViewDataset) is a partial view of the cleaned dataset after the preprocessing.

```{r tabViewDataset, echo=FALSE, warning=FALSE, message=FALSE}
#### A partial view of the cleaned dataset ####
tableCleanedData <-
  dfNewCoders[1:10,] %>%
  mutate_all(linebreak) %>%
  kable(caption = "A partial view of \\\\the cleaned dataset",
      booktabs = T,
      escape = F,
      "latex",
      col.names = linebreak(c("Gender", 
                              "Age",
                              "City\nPopulation",
                              "Commute\nTime",
                              "Income",
                              "Months\nProgramming",
                              "School\nDegree",
                              "Money For\nLearning"), align = "c")) %>%
  kable_classic(full_width = F)

tableCleanedData

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#### Descriptive statistics ####
stargazer::stargazer(data.frame(dfNewCoders), type = "text")

>>>>

## Description of Dataset
The original dataset used for this paper is obtained from `freeCodeCamp`’s GitHub page. The format of the dataset is a comma-separated values (CSV) file, which contains 136 columns and 18,175 observations. I selected 8 variables and cleaned the data using the R programming language [@citeR] and the `tidyverse` package [@cityTidyverse] and the `dplyr` package [@cityDplyr]. The selected variables are: Age, CityPopulation, CommuteTime, Gender,  Income, MoneyForLearning, MonthsProgramming, and SchoolDegree. The CityPopulation is the estimated number of city population of the recipient; the question asked was "About how many people live in your city?”, and there are three options to choose: “less than 100,000”, "between 100,000 and 1 million", and "more than 1 million". Since these answers were coded as strings, I converted them into numeric variables using the `recode` function of `dplyr` [@cityDplyr]. The answers for CommuteTime and SchoolDegree were also coded as strings in the original dataset, so I applied the same data cleaning process to the variables as I did with CityPopulation. Also, I omitted observations which have a missing value. Table \@ref(tab:tabViewDataset) is a partial view of the cleaned dataset after the preprocessing.

```{r tabViewDataset, echo=FALSE, warning=FALSE, message=FALSE}
#### A partial view of the cleaned dataset ####
tabCleanedData <-
  dfNewCoders[1:10,] %>%
  mutate_all(linebreak) %>%
  kable(caption = "A partial view of \\\\the cleaned dataset",
      booktabs = T,
      escape = F,
      "latex",
      col.names = linebreak(c("Gender", 
                              "Age",
                              "City\nPopulation",
                              "Commute\nTime",
                              "Income",
                              "Months\nProgramming",
                              "School\nDegree",
                              "Money For\nLearning"), align = "c")) %>%
  kable_classic(full_width = F)

tabCleanedData

```{r tabDescrStat, echo=FALSE, warning=FALSE, message=FALSE, results='asis'}
#### Descriptive statistics ####

stargazer::stargazer(data.frame(dfNewCoders), 
                     type = "latex", 
                     title = "Descriptive statistics for the cleaned dataset", 
                     header = FALSE,
                     single.row = TRUE)

@@
